### 2019-06-25 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Update and fix typos

% \vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $[K]$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(0) \sim \cU([K])$ and $C^j(0)=\mathrm{False}$ \\
              \For{$t = 1, \dots, T$}{
                  %
                  \uIf{$A^j(t-1) \notin \TopM(t)$}{
                    \uIf(\tcp*[f]{collision at previous step}){$C^j(t-1)$}{
                      $A^j(t) \sim \cU \left(\TopM(t)\right)$
                      \tcp*[f]{randomly switch}
                      }
                    \uElse(\tcp*[f]{randomly switch on an arm that had smaller UCB}){
                      $A^j(t) \sim \cU \left(\TopM(t) \cap \left\{k : U_k^j(t-1) \leq U^j_{A^j(t)}(t-1)\right\}\right)$
                    }
                  }
                  \uElse{
                    $A^j(t) = A^j(t-1)$
                    \tcp*[f]{stays on the same arm}
                  }
                  Play arm $A^j(t)$, get new observations (sensing and collision), \\
                  Compute the indices $U^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \RandTopM{} decentralized learning policy]{The \RandTopM{} decentralized learning policy (for an index policy $U^j$).}
          \label{algo:5:RandTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
% \vspace*{-5pt}  % XXX remove if problem

@@

% \vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $[K]$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(0) \sim \cU([K])$ and $C^j(0)=\mathrm{False}$ and $s^j(1)=\mathrm{False}$ \\
              \For{$t = 1, \dots, T$}{
                   \uIf(\tcp*[f]{transition $(3)$ or $(5)$}){
                      $A^j(t-1) \notin \TopM(t)$}
                    {
                      $A^j(t) \sim \cU \left(\TopM(t) \cap \left\{k : U_k^j(t-1) \leq U^j_{A^j(t)}(t-1)\right\}\right)$
                      \tcp*[f]{not empty} \\
                      % \tcp*[f]{randomly switch on an arm that had smaller UCB}
                      $s^j(t) = \mathrm{False}$
                      \tcp*[f]{aim at an arm with a smaller UCB at $t-1$}
                    }
                    \uElseIf(\tcp*[f]{collision and not fixed}){
                        $C^j(t-1)$ \emph{and} $\overline{s^j(t-1)}$}
                      {
                        $A^j(t) \sim \cU \left(\TopM(t)\right)$
                        \tcp*[f]{transition $(2)$} \\
                        $s^j(t) = \mathrm{False}$
                    }
                    \uElse(\tcp*[f]{transition $(1)$ or $(4)$}){
                      $A^j(t) = A^j(t-1)$ \tcp*[f]{stay on the previous arm} \\
                      $s^j(t) = \mathrm{True}$ \tcp*[f]{become or stay fixed on a ``chair''}
                    }
                  Play arm $A^j(t)$, get new observations (sensing and collision), \\
                  Compute the indices $U^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \MCTopM{} decentralized learning policy]{The \MCTopM{} decentralized learning policy (for an index policy $U^j$).}
          \label{algo:5:MCTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
% \vspace*{-5pt}  % XXX remove if problem

@@

%
% Regular plots of centralized regrets
%
\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K3_M2_T5000_N1000__4_algos/all_HistogramsRegret____env1-1_5016720151160452442.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.10\textwidth]{MP__K3_M3_T5000_N1000__4_algos/all_HistogramsRegret____env1-1_1035303196230283176.pdf}
  % \end{subfigure}
  \caption[Failure case of \Selfish]{Regret for $M=2$ players, $K=3$ arms, horizon $T=5000$, $1000$ repetitions and $\boldsymbol{\mu} = [0.1, 0.5, 0.9]$. Axis $x$ is for regret (different scale for each part), and the \textcolor{darkgreen}{green} curve for \Selfish{} shows a small probability of having a linear regret ($17$ cases of $R_T \geq T$, out of $1000$). The regret for the three other algorithms is very small for this problem, always smaller than $100$ here.}
  \label{fig:5:selfish_fail1}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

\begin{figure}[!b]
  \centering
  % \begin{subfigure}[!h]{0.85\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{0.85\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_HistogramsRegret____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players for $K=9$ arms, horizon $T=5000$, for $1000$ repetitions on a fixed problem]{Regret (in log-log scale), for $M=6$ players for $K=9$ arms, horizon $T=5000$, for $1000$ repetitions on problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$. \RandTopM{} (\textcolor{gold}{yellow} curve) outperforms \Selfish{} (\textcolor{darkgreen}{green}), both clearly outperform \rhoRand. The regret of \MCTopM{} is logarithmic, empirically with the same slope as the lower bound. The $x$ axis on the regret histograms have different scale for each algorithm.}
  \label{fig:5:MP__K9_M6_T10000_N1000__4_algos}
\end{figure}

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_2643359116089264295.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T10000_N200__4_algos/all_RegretCentralized_loglog____env1-1_2306423191427933958.pdf}
  % \end{subfigure}
  \caption[Regret for $M=2$ and $9$ players for $K=9$ arms, horizon $T=5000$, for a fixed problem]{Regret (in log-log scale), for $M=2$ and $9$ players for $K=9$ arms, horizon $T=5000$, for problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$] for problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$. In different settings, \RandTopM{} (\textcolor{gold}{yellow} curve) and \Selfish{} (\textcolor{darkgreen}{green}) can outperform each other, and always outperform \rhoRand. \MCTopM{} is always among the best algorithms, and for $M$ not too small, its regret seems logarithmic with a constant matching the lower bound.}
  \label{fig:5:MP__K9_M2-6-9_T10000_N200__4_algos}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{0.85\textwidth}
      \includegraphics[width=1.00\textwidth]{MP__K9_M3_T123456_N100__8_algos/all_RegretCentralized____env1-1_7803645526012310577.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{0.85\textwidth}
      \includegraphics[width=1.00\textwidth]{MP__K9_M3_T123456_N100__8_algos/all_RegretCentralized_semilogy____env1-1_7803645526012310577.pdf}
  % \end{subfigure}
  \caption[Regret for $M=3$ players for $K=9$ arms, horizon $T=123456$, for $100$ repetitions on a fixed problem]{Regret for $M=3$ players for $K=9$ arms, horizon $T=123456$, for $100$ repetitions on problem $\mu=[0.1,\dots,0.9]$. With a perfect knowledge on the horizon and the gap ($\Delta=0.1$ here) and by using the parameters suggested from their respective articles, \MEGA{} and \MusicalChair{} perform badly, even in this simple setting. The first two \MusicalChair{} instances use the optimal $T_0$ value from \cite{Rosenski16}, with $\varepsilon$ taken slightly smaller than the gap $\Delta$ ($\varepsilon=0.99 \Delta$), and respectively with $\delta=0.5$ and $\delta=0.1$, for which the regret can bounded with probability $0.5$ and $0.9$ respectively. The third instance uses the optimal $T_0$ corresponding to $\delta=1/T$, that is guaranteed to have an expected regret of order $\log(T)$. The log-$y$ scale is used to easily differentiate between the different algorithms, and highlight that our proposal (in \textcolor{gold}{yellow $\nabla$}) outperform both \MEGA{} and \MusicalChair{} by three orders of magnitudes!}
  \label{fig:5:MP__K9_M3_T123456_N100__8_algos}
\end{figure}

%
% Regular plots of centralized regrets
%
\begin{figure}[!t]
  % \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled]{Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \rhoRand{} (top \textcolor{blue}{blue} curve) is outperformed by the other algorithms (and the gain increases with $M$). \MCTopM{} (bottom \textcolor{gold}{yellow}) outperforms all the other algorithms is most cases.}
  % \label{fig:5:MP__K9_M2-6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  \label{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
      % \includegraphics[width=1.00\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_HistogramsRegret____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  \caption[Regret for $M=2$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled]{Regret for $M=2$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \rhoRand{} (top \textcolor{blue}{blue}) is outperformed by the other algorithms (and the gain increases when $M$ increases), which all perform similarly in such configurations. Note that the (small) tail of the histograms come from complicated problems $\boldsymbol{\mu}$ and not failure cases.}
  \label{fig:5:MP__K9_M2_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T5000_N500__4_algos/all_RegretCentralized____env1-1_3892966382091165662.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T5000_N500__4_algos/all_HistogramsRegret____env1-1_3892966382091165662.pdf}
  % \end{subfigure}
  \caption[Regret for $M=K=9$, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled]{Regret for $M=K=9$, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. This extreme case $M=K$ shows the drastic difference of behavior between \RandTopM{} and \MCTopM, having constant regret, and \rhoRand{} and \Selfish, having large regret.}
  \label{fig:5:MP__K9_M9_T5000_N500__4_algos__all_HistogramsRegret}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

>>>>

% \vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $[K]$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(0) \sim \cU([K])$ and $C^j(0)=\mathrm{False}$ \\
              \For{$t = 1, \dots, T$}{
                  %
                  \uIf{$A^j(t-1) \notin \TopM(t)$}{
                    \uIf(\tcp*[f]{collision at previous step}){$C^j(t-1)$}{
                      $A^j(t) \sim \cU \left(\TopM(t)\right)$
                      \tcp*[f]{randomly switch}
                      }
                    \uElse(\tcp*[f]{randomly switch on an arm that had smaller UCB}){
                      $A^j(t) \sim \cU \left(\TopM(t) \cap \left\{k : U_k^j(t-1) \leq U^j_{A^j(t)}(t-1)\right\}\right)$
                    }
                  }
                  \uElse{
                    $A^j(t) = A^j(t-1)$
                    \tcp*[f]{stays on the same arm}
                  }
                  Play arm $A^j(t)$, get new observations (sensing and collision), \\
                  Compute the indices $U^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \RandTopM{} decentralized learning policy.]{The \RandTopM{} decentralized learning policy (for an index policy $U^j$).}
          \label{algo:5:RandTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
% \vspace*{-5pt}  % XXX remove if problem

@@

% \vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $[K]$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(0) \sim \cU([K])$ and $C^j(0)=\mathrm{False}$ and $s^j(1)=\mathrm{False}$ \\
              \For{$t = 1, \dots, T$}{
                   \uIf(\tcp*[f]{transition $(3)$ or $(5)$}){
                      $A^j(t-1) \notin \TopM(t)$}
                    {
                      $A^j(t) \sim \cU \left(\TopM(t) \cap \left\{k : U_k^j(t-1) \leq U^j_{A^j(t)}(t-1)\right\}\right)$
                      \tcp*[f]{not empty} \\
                      % \tcp*[f]{randomly switch on an arm that had smaller UCB}
                      $s^j(t) = \mathrm{False}$
                      \tcp*[f]{aim at an arm with a smaller UCB at $t-1$}
                    }
                    \uElseIf(\tcp*[f]{collision and not fixed}){
                        $C^j(t-1)$ \emph{and} $\overline{s^j(t-1)}$}
                      {
                        $A^j(t) \sim \cU \left(\TopM(t)\right)$
                        \tcp*[f]{transition $(2)$} \\
                        $s^j(t) = \mathrm{False}$
                    }
                    \uElse(\tcp*[f]{transition $(1)$ or $(4)$}){
                      $A^j(t) = A^j(t-1)$ \tcp*[f]{stay on the previous arm} \\
                      $s^j(t) = \mathrm{True}$ \tcp*[f]{become or stay fixed on a ``chair''}
                    }
                  Play arm $A^j(t)$, get new observations (sensing and collision), \\
                  Compute the indices $U^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \MCTopM{} decentralized learning policy.]{The \MCTopM{} decentralized learning policy (for an index policy $U^j$).}
          \label{algo:5:MCTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
% \vspace*{-5pt}  % XXX remove if problem

@@

%
% Regular plots of centralized regrets
%
\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K3_M2_T5000_N1000__4_algos/all_HistogramsRegret____env1-1_5016720151160452442.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.10\textwidth]{MP__K3_M3_T5000_N1000__4_algos/all_HistogramsRegret____env1-1_1035303196230283176.pdf}
  % \end{subfigure}
  \caption[Failure case of \Selfish.]{Regret for $M=2$ players, $K=3$ arms, horizon $T=5000$, $1000$ repetitions and $\boldsymbol{\mu} = [0.1, 0.5, 0.9]$. Axis $x$ is for regret (different scale for each part), and the \textcolor{darkgreen}{green} curve for \Selfish{} shows a small probability of having a linear regret ($17$ cases of $R_T \geq T$, out of $1000$). The regret for the three other algorithms is very small for this problem, always smaller than $100$ here.}
  \label{fig:5:selfish_fail1}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

\begin{figure}[!b]
  \centering
  % \begin{subfigure}[!h]{0.85\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{0.85\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_HistogramsRegret____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players for $K=9$ arms, horizon $T=5000$, for $1000$ repetitions on a fixed problem.]{Regret (in log-log scale), for $M=6$ players for $K=9$ arms, horizon $T=5000$, for $1000$ repetitions on problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$. \RandTopM{} (\textcolor{gold}{yellow} curve) outperforms \Selfish{} (\textcolor{darkgreen}{green}), both clearly outperform \rhoRand. The regret of \MCTopM{} is logarithmic, empirically with the same slope as the lower bound. The $x$ axis on the regret histograms have different scale for each algorithm.}
  \label{fig:5:MP__K9_M6_T10000_N1000__4_algos}
\end{figure}

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_2643359116089264295.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M6_T10000_N1000__4_algos/all_RegretCentralized_loglog____env1-1_8200873569864822246.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T10000_N200__4_algos/all_RegretCentralized_loglog____env1-1_2306423191427933958.pdf}
  % \end{subfigure}
  \caption[Regret for $M=2$ and $9$ players for $K=9$ arms, horizon $T=5000$, for a fixed problem.]{Regret (in log-log scale), for $M=2$ and $9$ players for $K=9$ arms, horizon $T=5000$, for problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$] for problem $\boldsymbol{\mu}=[0.1,\dots,0.9]$. In different settings, \RandTopM{} (\textcolor{gold}{yellow} curve) and \Selfish{} (\textcolor{darkgreen}{green}) can outperform each other, and always outperform \rhoRand. \MCTopM{} is always among the best algorithms, and for $M$ not too small, its regret seems logarithmic with a constant matching the lower bound.}
  \label{fig:5:MP__K9_M2-6-9_T10000_N200__4_algos}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{0.85\textwidth}
      \includegraphics[width=1.00\textwidth]{MP__K9_M3_T123456_N100__8_algos/all_RegretCentralized____env1-1_7803645526012310577.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{0.85\textwidth}
      \includegraphics[width=1.00\textwidth]{MP__K9_M3_T123456_N100__8_algos/all_RegretCentralized_semilogy____env1-1_7803645526012310577.pdf}
  % \end{subfigure}
  \caption[Regret for $M=3$ players for $K=9$ arms, horizon $T=123456$, for $100$ repetitions on a fixed problem.]{Regret for $M=3$ players for $K=9$ arms, horizon $T=123456$, for $100$ repetitions on problem $\mu=[0.1,\dots,0.9]$. With a perfect knowledge on the horizon and the gap ($\Delta=0.1$ here) and by using the parameters suggested from their respective articles, \MEGA{} and \MusicalChair{} perform badly, even in this simple setting. The first two \MusicalChair{} instances use the optimal $T_0$ value from \cite{Rosenski16}, with $\varepsilon$ taken slightly smaller than the gap $\Delta$ ($\varepsilon=0.99 \Delta$), and respectively with $\delta=0.5$ and $\delta=0.1$, for which the regret can bounded with probability $0.5$ and $0.9$ respectively. The third instance uses the optimal $T_0$ corresponding to $\delta=1/T$, that is guaranteed to have an expected regret of order $\log(T)$. The log-$y$ scale is used to easily differentiate between the different algorithms, and highlight that our proposal (in \textcolor{gold}{yellow $\nabla$}) outperform both \MEGA{} and \MusicalChair{} by three orders of magnitudes!}
  \label{fig:5:MP__K9_M3_T123456_N100__8_algos}
\end{figure}

%
% Regular plots of centralized regrets
%
\begin{figure}[!t]
  % \centering
  % \begin{subfigure}[!h]{0.49\textwidth}
  %   \includegraphics[width=1.00\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % % ~
  % \begin{subfigure}[!h]{0.49\textwidth}
    \includegraphics[width=1.10\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
  % \end{subfigure}
  \caption[Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=6$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \rhoRand{} (top \textcolor{blue}{blue} curve) is outperformed by the other algorithms (and the gain increases with $M$). \MCTopM{} (bottom \textcolor{gold}{yellow}) outperforms all the other algorithms is most cases.}
  % \label{fig:5:MP__K9_M2-6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  \label{fig:5:MP__K9_M6_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

@@

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_RegretCentralized____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
      % \includegraphics[width=1.00\textwidth]{MP__K9_M6_T5000_N500__4_algos/all_RegretCentralized____env1-1_8318947830261751207.pdf}
      \includegraphics[width=1.10\textwidth]{MP__K9_M2_T5000_N500__4_algos/all_HistogramsRegret____env1-1_3251433209347345969.pdf}
  % \end{subfigure}
  \caption[Regret for $M=2$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=2$ players, $K=9$ arms, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. \rhoRand{} (top \textcolor{blue}{blue}) is outperformed by the other algorithms (and the gain increases when $M$ increases), which all perform similarly in such configurations. Note that the (small) tail of the histograms come from complicated problems $\boldsymbol{\mu}$ and not failure cases.}
  \label{fig:5:MP__K9_M2_T5000_N500__4_algos__all_RegretCentralized__BayesianProblems}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

\begin{figure}[!t]
  \centering
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T5000_N500__4_algos/all_RegretCentralized____env1-1_3892966382091165662.pdf}
  % \end{subfigure}
  % ~
  % \begin{subfigure}[!h]{1.00\textwidth}
      \includegraphics[width=1.10\textwidth]{MP__K9_M9_T5000_N500__4_algos/all_HistogramsRegret____env1-1_3892966382091165662.pdf}
  % \end{subfigure}
  \caption[Regret for $M=K=9$, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled.]{Regret for $M=K=9$, horizon $T=5000$, against $500$ problems $\boldsymbol{\mu}$ uniformly sampled in $[0,1]^K$. This extreme case $M=K$ shows the drastic difference of behavior between \RandTopM{} and \MCTopM, having constant regret, and \rhoRand{} and \Selfish, having large regret.}
  \label{fig:5:MP__K9_M9_T5000_N500__4_algos__all_HistogramsRegret}
  % \vspace*{-15pt}  % XXX remove if problem
\end{figure}
